Statistical Mechanics Informed Neural Networks for Solar Wind modeling

### 2024-11-13 paper/main.tex
default

\cite{kumar2023physicsinformedneuralnetworks}

>>>>

Regarding Vlasov-Maxwell modeling with physics informed neural networks, this paper constitutes the first machine learning approach intersecting both this theory and the novel PDE solving scheme proposed by PINNs. \cite{kumar2023physicsinformedneuralnetworks} It employs the model onto fusion modeling within the colisionless constraint.
